Under-ice acoustic navigation using real-time model-aided range estimation

### 2021-12-13 rebuttal/rebuttal-letter/trunk-rebuttal.tex

\documentclass{article}
	\def\papertitle{Under-ice acoustic navigation using real-time model-aided range estimation}
	\def\authors{E. Bhatt, O. V\'{i}quez, H. Schmidt}
	\def\journal{Journal of the Acoustical Society of America}
	\def\doi{}

\input{../p-rebuttal-letter.tex}

Dear Editors,

We thank the reviewers and editor for their thoughtful feedback and comments in improving this work. We have significantly restructured the manuscript along several suggestions to separate the real-time navigation methodology, the real-time positioning results (Mininum Bounce Criteria), and the post-processing re-positioning improvement (Nearest Bounce Criteria). We have also introduced that language (navigation, positioning, and re-positioning) more explicitly to avoid confusion and better contextualize our contribution.

@@

% table of contents
\renewcommand{\contentsname}{}
\begingroup
\let\pagebreak\relax
\setcounter{tocdepth}{1}
\tableofcontents
\endgroup

%% ------- COMMENTS FROM REVIEWER ONE ------ %%
\section{Reviewer One}

	\subsection*{Summary}

	\ebline{This paper demonstrates how a positioning system over \~1.5-3 km of range achieves 11 m of positioning uncertainty. The work demonstrates how a single group velocity calculated from acoustic rays predicted by BELLHOP can be used to estimate ranges to be used in a LBL network for positioning. The data presented are from transceivers on fixed ice-tethered buoys but the system could also be implemented on an autonomous underwater vehicle.}

	This summary captures key results presented in the paper. However, we note that the system was successfully deployed on an underwater vehicle during ICEX20. The results from this work are specifically limited to the methodology behind calculating a single group velocity, which can be quantified through beacon-to-beacon communications.

@@

	\subsection*{Overall Comments}

	\reviewer{}{The claims made in the abstract need to be better supported by the data presented or else tempered a bit. What is demonstrated here is not real-time navigation on a vehicle, but calculation of a handful of short fixed ranges from ice-tethered buoys. The limited data presented here begs more discussion with regards to how applicable the algorithm would be in normal vehicle operation and to navigation of the vehicle, as there were limited ranges between the beacons. What depths does the vehicle typically operate at and what is the maximum range from the beacons?  The abstract stresses real-time results, but the real-time results are just 3 paragraphs, and the paper mostly concentrates on post-processing results.}

	We have tempered the claims in the abstract to reflect the limitations of the dataset collected and the transferability of the analysis in this paper.
	We have also included a discussion of how these results might compare for various depths and ranges during vehicle operations (see \hl{XXX}).

	With respect to the concentrating on real-time results versus post-processing results, we would point out that the AUV was deployed through a hydrohole from Topside and due to a disk error, stalled underneath the ice surface while transmitting its perceived location.
	The AUV was found within a meter from its reported location, which serves as strong (but qualitative) evidence of the navigation performance provided by the single group velocity calculation.
	Work currently review in the Journal of Field Robotics details the other components to vehicle navigation (DVL-aided INS and a vehicle flight model) along with the magnitude of position corrections.

	Given that our vehicle navigation data only has one GPS point to compare to, we use the beacon-to-beacon communications as a natural experiment to compare the effectiveness of the real-time NBC method.
	The real-time section is small because only one modem at a time ran the vehicle behavior to calculate these acoustic pseudoranges.
	A robust comparison is tainted by the mismatch of experimental conditions in estimated sound speed environment and source / receiver position.

	We extended the dataset to all possible communication events through the same automated pipeline to decouple the effects of the sound speed environment from source and receiver position. This is in effect no different than running the computation during the field; the real-time NBC data is a subset of the post-processed NBC data.

	While post-processing, we began to see a pattern of range overestimation using the NBC method. Thus, we developed the Minimal Bounce Criteria instead and ran it through the same pipeline, subject to the same computational constraints.

	By comparing the errors between these two pseudorange estimation methods, we noticed a surprising underlying pattern compared to the ground truth GPS data.
	Further investigation suggests there is noise in the GPS measurement that is not incurred in the travel time measurement that informs the acoustic range estimation.

	The manuscript has been significantly restructured to separate analyses along this narrative.

	\reviewer{}{The hypothesis is stated in the discussion section lines 515 and following: “We hypothesize and validate that the embedded stochastic prediction of a single group velocity is a smoothly varying function of range, source, and receiver depth pairings as well as multipath structure.”  I am not convinced that the few short fixed ranges presented here validate this hypothesis.  Lines 248 and following indicate how the system should track a continuously changing group velocity, but this is not demonstrated with the few fixed ranges presented here.  Also, it would be good to state this hypothesis more clearly earlier in the manuscript.}
	We agree that a few short fixed ranges do not validate this hypothesis. With the overarching motivation and design of LBL navigation, we have recast this hypothesis as an assumption. We would note, again, that the vehicle navigation performance would better determine a continuously changing group velocity, but this data would have no way of being verified.

@@

	\lreviewer{Figure 5}{}{What is the point labeled u=751 m/s that appears to fall around 1424 m/s?}

	\lreviewer{Table II}{}{Might this information be portrayed better by a box plot?}

	\subsection*{Minor Edits}

	\lreviewer{Fig. 2 and 3}{}{Fig 2 refers to central node position as Topside and Fig. 3 as Camp Seadragon. Suggest standardizing.}
	Thank you. We have standardized this to Topside.

	\lreviewer{lines 311, 359}{}{'Data' should be plural.}
	Thank you. This has been corrected.

@@

	\lreviewer{Figure 6}{v1:fig:rangeError}{Suggest including receiver depth along with source depth in the title as they are both important in distinguishing between the cases.}

	\lreviewer{Table I}{v1:tab:rangeErrorInSitu}{Table I indicates direction errors are positive. Please note the sign convention in the caption.}
	{\color{blue} caption is correct but text references an ``overstimation'' of range that is not obvious given absolute error shown.}

	\lreviewer{Table II}{v1:tab:rangeErrorV1V2}{‘range estimation error metrics’ rather than ‘range estimation metrics’?}
	Agreed. We have made the suggested change.

	\lreviewer{Table II and III}{}{Suggest removing ‘algorithm’ label.  Also substitute ‘MBC’ and ‘NBC’ for minimal and nearest to match the text.}
	Agreed. We have made the suggested changes.

	\lreviewer{}{}{There are several figures and tables which are not referenced properly (Line 305, 391, 411)}
	Thank you. This has been corrected.

@@

%% ------- COMMENTS FROM REVIEWER TWO ------ %%

\section{Reviewer Two}

	\lreviewer{line 7}{v1:2.1}{'Beaufort Lens' This is not yet a scientific term, suggest finding descriptive terms to use. What comprises the 'lens'? The Pacific Summer Water is the warm layer.}

	\lreviewer{line 10}{v1:2.2}{'GPS aided', do you mean GPS-navigated?}
	We have changed this to ``GPS-linked'' because navigation implies self-movement.

### 2021-12-13 manuscript/main.tex
starting to write edits

\begin{abstract}
Almost all underwater navigation paradigms rely on the conversion of recorded travel time into range to compute a trilateration solution.
For real-time navigation, this conversion is treated deterministically.
For positioning in post-processing, more computationally and/or labor intensive modeling methods are often employed to reduce the uncertainty driven by multipath arrivals.
\llabel{2.1} An autonomous underwater vehicle deployment in March 2020 in the Beaufort Sea faced significant operational challenges with a total ice-covered environment and complex acoustic propagation via the Beaufort Lens.
\llabel{2.2} We implement an embedded, stochastic, ray-based prediction of the horizontal group velocity and validate its performance with communication events between GPS-aided beacons, achieving a pseudorange mean absolute error of 11 m.
\llabel{2.3} In post-processing, we introduce a multipath criterion and achieve ranging performance that rivals GPS.
To our knowledge, these results are the first field experiment to demonstrate a real-time, physics-based data processing to minimize ranging error in underwater navigation.
\end{abstract}

@@

This method selects a different group velocity based on the multipath arrival structure, as the detected arrival is not always the first arrival or the direct path and could even be masked by noise or blocked temporarily \citep{deffenbaugh_acoustic_1996}.
We manually cap the number of bounces to 4 because of the smaller operational scale and the attenuation accrued with many surface interactions.
Bottom bounces are not encoded separately because of ray's tendency to refract upward, not due to information limitations. 
\llabel{1.17} In addition, for a more consistent comparison, the local sparse grid is standardized as 11$\times$11 points over 10 m in range and 20 m in depth, which is similar to those from the vehicle logs.
The extra size in depth addresses the computational limitations of how time-bounded eigenrays seem to stack vertically in the water column, as shown in Fig \ref{fig:rays3env-zs30}.

@@

\begin{table}[h!]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{r|c|c|c|c|c}
SSP & Count & ~Mean [m] & ~Median [m] & ~STD [m] & ~Max [m] \\ \hline
Baseline & 243 & 11.38 & 11.96 & 4.23 & 23.95 \\ 
Chosen weights & 568 & 11.36 & 11.40 & 8.12 & 26.0 \\
\toprule
\end{tabular}
\caption[Range estimation error for \textit{in situ} events]{The range estimation error for \textit{in situ} events. The error here is presented as the absolute, not directional, error. Almost all directional errors, however, are positive.}
\label{tab:rangeErrorInSitu}
\end{table}

@@

Overall, analysis shows that the higher multipath classification produces more accurate range estimates, likely driven by a tighter bundle of rays.
However, that data is too small to draw significant conclusions.
\llabel{1.19} Discontinuities in multipath classification verify our hypothesis for its importance to a smoothly varying group velocity, as shown in the cluster for a receiver depth of 30 m, where HYCOM jumps from one to two bounces amidst the baseline SSP and weighted SSP smoothly increasing while consistently seeing two and three bounces, respectively.

@@

All the events are on the unshaded region of the plots\textemdash the MBC has a systemic overestimation, which is reduced via NBC as events straddle the x-axis.
The improvement from MBC to NBC is most evident for the realistic sound speed; while the HYCOM SSP improves from a median absolute range error of 6.41 to 4.61 m, the baseline SSP improves from 10.30 to 2.27 m, and the weighted SSP improves from 13.28 to 2.12 m.
Table \ref{tab:rangeErrorPost} shows further statistics on the absolute range error by SSP and group velocity algorithm.
The order of magnitude improvement in the ducted SSPs demonstrate the effectiveness of the algorithm exploiting the multipath conditions.

@@

\begin{table}[h!]
\renewcommand{\arraystretch}{1.5}
\centering
\begin{tabular}{r|cc|cc|cc}\toprule
 & \multicolumn{2}{c|}{\textbf{Baseline} } & \multicolumn{2}{c|}{\textbf{Chosen Weights} } & \multicolumn{2}{c}{\textbf{HYCOM}} \\
 algorithm & \cellcolor[HTML]{EFEFEF}minimal & nearest & \cellcolor[HTML]{EFEFEF} minimal& nearest & \cellcolor[HTML]{EFEFEF}minimal & nearest \\ \hline
 minimum [m] 	& \cellcolor[HTML]{EFEFEF}0.01 & 0.00	& \cellcolor[HTML]{EFEFEF}0.00 	& 0.00 	& \cellcolor[HTML]{EFEFEF}0.11 & 0.01 \\
 25th \% [m]   & \cellcolor[HTML]{EFEFEF}4.96 & 0.99	& \cellcolor[HTML]{EFEFEF}6.26 	& 0.95 	& \cellcolor[HTML]{EFEFEF}3.30 & 2.25 \\   
 median [m]		& \cellcolor[HTML]{EFEFEF}10.30 & 2.27 	& \cellcolor[HTML]{EFEFEF}13.28 & 2.12 	& \cellcolor[HTML]{EFEFEF}6.41 & 4.61 \\
 75th \% [m]   & \cellcolor[HTML]{EFEFEF}15.81 & 5.51 	& \cellcolor[HTML]{EFEFEF}19.75 & 4.11 	& \cellcolor[HTML]{EFEFEF}10.92 & 7.46 \\
 maximum [m]    & \cellcolor[HTML]{EFEFEF}22.52 & 14.96 & \cellcolor[HTML]{EFEFEF}1491  & 20.21 & \cellcolor[HTML]{EFEFEF}19.55 & 15.81 \\
 \toprule
\end{tabular}
\caption[Comparison of post-processing range estimation algorithms across all events]{A comparison of range estimation metrics for each sound speed source and group velocity estimation algorithm for all 1283 beacon to beacon events via post-processing. The 0th (minimum), 25th, 50th (median), 75th, and 100th (maximum) percentiles are shown to the range resolution afforded by the WHOI Micro-Modem. There are a few outliers that drive the mean to be higher than the median.}
\label{tab:rangeErrorV1V2}
\end{table}

@@

As shown in table \ref{tab:rangeErrorPost}, there is a striking maximum range error of 1491 m for the weighted SSP in the minimal bounce criteria.
This section isolates the events that encompass that outlier for further examination, summarized in table \ref{tab:rangeErrorPostExplanation}.
There are 10 events from South transmitting at 30 m depth to North receiving at 30 m depth.
The OWTT spread is from 2.1958 to 2.1963 s; the naive group velocity is 1429.3 to 1430.1 m/s; and the GPS-tracked range is from 3138.54 m to 3140.87 m.
This example ends up being an excellent case study for how sound speed and multipath fidelity work in concert to minimize range error.

\begin{table}[h!]
\renewcommand{\arraystretch}{1.5}
\centering
\begin{tabular}{r|cc|cc|cc}\toprule
 & \multicolumn{2}{c|}{\textbf{Baseline} } & \multicolumn{2}{c|}{\textbf{Chosen Weights} } & \multicolumn{2}{c}{\textbf{HYCOM}} \\
 algorithm & \cellcolor[HTML]{EFEFEF}minimal & nearest & \cellcolor[HTML]{EFEFEF} minimal& nearest & \cellcolor[HTML]{EFEFEF}minimal & nearest \\ \hline
 \# bounces 				& \cellcolor[HTML]{EFEFEF}1 		& 3 		& \cellcolor[HTML]{EFEFEF}1 		& 4 		& \cellcolor[HTML]{EFEFEF}0 	 & 2 \\
 mean OWTT [s] 				& \cellcolor[HTML]{EFEFEF}2.1853 	& 2.1943 	& \cellcolor[HTML]{EFEFEF}4.1812 	& 2.1955 	& \cellcolor[HTML]{EFEFEF}2.1877 & 2.1902 \\
 mean group velocity [m/s] 	& \cellcolor[HTML]{EFEFEF}1436.7 	& 1430.8 	& \cellcolor[HTML]{EFEFEF}750.88 	& 1430.0 	& \cellcolor[HTML]{EFEFEF}1435.1 & 1433.4 \\
 range error [m] 			& \cellcolor[HTML]{EFEFEF}15.4 		& 2.39 	 	& \cellcolor[HTML]{EFEFEF}-1491 	& 0.77 		& \cellcolor[HTML]{EFEFEF}11.9 & 8.30 \\
 \toprule
\end{tabular}
\caption[Further look at algorithm differences for one beacon to beacon pairing]{A comparison of range estimation metrics for each sound speed source and group velocity estimation algorithm on all 10 communication events between North at 30 m \& South at 30 m.}
\label{tab:rangeErrorPostExplanation}
\end{table}

>>>>

% The motivation behind this work is to improve the standard LBL navigation’s conversion of travel time to range for an under-ice environment in a way that could be generalized to any acoustic waveguide. To do this, we introduce the Minimal Bounce Criteria method to operationalize real-time acoustic modeling into an effective horizontal group velocity estimate.

% 	This system was implemented on an autonomous underwater vehicle (AUV) on multiple missions, including an 11 km untethered, under-ice deployment, in March 2020. The AUV was deployed through a hydrohole from Topside and due to a disk error, stalled underneath the ice surface while transmitting its perceived location. The AUV was found within a meter away from its reported location, which serves as strong (but qualitative) evidence of the navigation performance provided by the single group velocity calculation. Because the navigation updates throughout the AUV mission have no GPS ground truth to compare to, this paper evaluates the same system performance across the GPS-navigated LBL beacons.

% 	The real-time error from the Nearest Bounce Criteria (NBC) achieves a mean absolute positioning error of 11 m. Upon further evaluation of the acoustic events, the Minimal Bounce Criteria (MBC) is run in the same automated pipeline in post-processing (akin to real-time computational constraints and needs) and achieves an error of roughly 3 m.

% 	Both the NBC and MBC pseudorange estimations are compared to the GPS data on the LBL beacons. The error itself is small and the pattern of error exhibited indicates that the GPS ground truth data has significant noise (drift) that is not replicated by either pseudorange estimation method. For the MBC in particular, the post-processing error is within the precision of the GPS sensor, suggesting that its performance rivals that of GPS.

\begin{abstract}
The long baseline (LBL) underwater navigation paradigm relies on the conversion of recorded travel time to range to trilaterate for position.
For real-time navigation, this conversion assumes an isovelocity sound speed.
For re-navigation in post-processing, computationally and/or labor intensive acoustic modeling may be employed to reduce uncertainty driven by multipath arrivals.
This work demonstrates an embedded, ray-based prediction method of the effective horizontal group speed to minimize vehicle position error.
\llabel{2.1} This method, the Minimal Bounce Criteria (MBC), was implemented for a small scale AUV-LBL system in March 2020, in the Beaufort Sea, in total under-ice conditions and a double ducted acoustic propagation environment.
The vehicle was successfully deployed and recovered.
\llabel{2.2} Given the lack of GPS data throughout the vehicle's mission, however, the localization performance is quantified between GPS-linked beacon-to-beacon connections where a single beacon ran the vehicle's navigation stack.
The real-time positioning error is roughly 11 meters at distances up to 3 km.
In post-processing, the dataset is extended to all possible beacon-to-beacon events.
The localization performance is reevaluated with an operationally equivalent navigation stack using modeled, historical, and data-based sound speed profiles for the MBC and for a new method, the Nearest Bounce Criteria (NBC).
The best performing median re-positioning errors are roughly 10 and 2 meters, respectively.
\llabel{2.3} Further investigation suggests that the GPS ground truth data have some noise that is not reciprocated in either acoustic localization method.

% Almost all underwater navigation paradigms rely on the conversion of recorded travel time into range to compute a trilateration solution.
% For real-time navigation, this conversion is treated deterministically.
% For positioning in post-processing, more computationally and/or labor intensive modeling methods are often employed to reduce the uncertainty driven by multipath arrivals.
% \llabel{2.1} An autonomous underwater vehicle deployment in March 2020 in the Beaufort Sea faced significant operational challenges with a total ice-covered environment and complex acoustic propagation via the Beaufort Lens.
% \llabel{2.2} We implement an embedded, stochastic, ray-based prediction of the horizontal group velocity and validate its performance with communication events between GPS-aided beacons, achieving a pseudorange mean absolute error of 11 m.
% \llabel{2.3} In post-processing, we introduce a multipath criterion and achieve ranging performance that rivals GPS.
% To our knowledge, these results are the first field experiment to demonstrate a real-time, physics-based data processing to minimize ranging error in underwater navigation.
\end{abstract}

@@

This method selects a different group velocity based on the multipath arrival structure, as the detected arrival is not always the first arrival or the direct path and could even be masked by noise or blocked temporarily \citep{deffenbaugh_acoustic_1996}.
We manually cap the number of bounces to 4 because of the smaller operational scale and the attenuation accrued with many surface interactions.
Bottom bounces are not encoded separately because of ray's tendency to refract upward, not due to information limitations. 
\llabel{1.17} In addition, for a more consistent comparison, the local sparse grid is standardized as 11$\times$11 points over 10 m in range and 20 m in depth, which is similar to those from the vehicle logs.
The extra size in depth addresses the computational limitations of how time-bounded eigenrays seem to stack vertically in the water column, as shown in Fig \ref{fig:raytrace-zs30}.

@@

\begin{table}[h!]
\renewcommand{\arraystretch}{1.3}
\centering
\begin{tabular}{r|c|c|c|c|c}
SSP & Count & ~Mean [m] & ~Median [m] & ~STD [m] & ~Max [m] \\ \hline
Baseline & 243 & 11.38 & 11.96 & 4.23 & 23.95 \\ 
Chosen weights & 568 & 11.36 & 11.40 & 8.12 & 26.0 \\
\toprule
\end{tabular}
\caption[Range estimation error for \textit{in situ} events]{The range estimation error metrics for \textit{in situ} events. The error here is presented as the absolute, not directional, error. Almost all directional errors, however, are positive.}
\label{tab:rangeErrorInSitu}
\end{table}

@@

Overall, analysis shows that the higher multipath classification produces more accurate range estimates, likely driven by a tighter bundle of rays.
However, that data are too small to draw significant conclusions.
\llabel{1.19} Discontinuities in multipath classification verify our hypothesis for its importance to a smoothly varying group velocity, as shown in the cluster for a receiver depth of 30 m, where HYCOM jumps from one to two bounces amidst the baseline SSP and weighted SSP smoothly increasing while consistently seeing two and three bounces, respectively.

@@

All the events are on the unshaded region of the plots\textemdash the MBC has a systemic overestimation, which is reduced via NBC as events straddle the x-axis.
The improvement from MBC to NBC is most evident for the realistic sound speed; while the HYCOM SSP improves from a median absolute range error of 6.41 to 4.61 m, the baseline SSP improves from 10.30 to 2.27 m, and the weighted SSP improves from 13.28 to 2.12 m.
Table \ref{tab:rangeErrorV1V2} shows further statistics on the absolute range error by SSP and group velocity algorithm.
The order of magnitude improvement in the ducted SSPs demonstrate the effectiveness of the algorithm exploiting the multipath conditions.

@@

\begin{table}[h!]
\renewcommand{\arraystretch}{1.5}
\centering
\begin{tabular}{r|cc|cc|cc}\toprule
 & \multicolumn{2}{c|}{\textbf{Baseline} } & \multicolumn{2}{c|}{\textbf{Chosen Weights} } & \multicolumn{2}{c}{\textbf{HYCOM}} \\
  & \cellcolor[HTML]{EFEFEF}MBC & NBC & \cellcolor[HTML]{EFEFEF} MBC& NBC & \cellcolor[HTML]{EFEFEF}MBC & NBC \\ \hline
 minimum [m] 	& \cellcolor[HTML]{EFEFEF}0.01 & 0.00	& \cellcolor[HTML]{EFEFEF}0.00 	& 0.00 	& \cellcolor[HTML]{EFEFEF}0.11 & 0.01 \\
 25th \% [m]   & \cellcolor[HTML]{EFEFEF}4.96 & 0.99	& \cellcolor[HTML]{EFEFEF}6.26 	& 0.95 	& \cellcolor[HTML]{EFEFEF}3.30 & 2.25 \\   
 median [m]		& \cellcolor[HTML]{EFEFEF}10.30 & 2.27 	& \cellcolor[HTML]{EFEFEF}13.28 & 2.12 	& \cellcolor[HTML]{EFEFEF}6.41 & 4.61 \\
 75th \% [m]   & \cellcolor[HTML]{EFEFEF}15.81 & 5.51 	& \cellcolor[HTML]{EFEFEF}19.75 & 4.11 	& \cellcolor[HTML]{EFEFEF}10.92 & 7.46 \\
 maximum [m]    & \cellcolor[HTML]{EFEFEF}22.52 & 14.96 & \cellcolor[HTML]{EFEFEF}1491  & 20.21 & \cellcolor[HTML]{EFEFEF}19.55 & 15.81 \\
 \toprule
\end{tabular}
\caption[Comparison of post-processing range estimation algorithms across all events]{A comparison of range estimation metrics for each sound speed source and group velocity estimation algorithm for all 1283 beacon to beacon events via post-processing. The 0th (minimum), 25th, 50th (median), 75th, and 100th (maximum) percentiles are shown to the range resolution afforded by the WHOI Micro-Modem. There are a few outliers that drive the mean to be higher than the median.}
\label{tab:rangeErrorV1V2}
\end{table}

@@

As shown in table \ref{tab:rangeErrorV1V2}, there is a striking maximum range error of 1491 m for the weighted SSP in the minimal bounce criteria.
This section isolates the events that encompass that outlier for further examination, summarized in table \ref{tab:rangeErrorPostExplanation}.
There are 10 events from South transmitting at 30 m depth to North receiving at 30 m depth.
The OWTT spread is from 2.1958 to 2.1963 s; the naive group velocity is 1429.3 to 1430.1 m/s; and the GPS-tracked range is from 3138.54 m to 3140.87 m.
This example ends up being an excellent case study for how sound speed and multipath fidelity work in concert to minimize range error.

\begin{table}[h!]
\renewcommand{\arraystretch}{1.5}
\centering
\begin{tabular}{r|cc|cc|cc}\toprule
 & \multicolumn{2}{c|}{\textbf{Baseline} } & \multicolumn{2}{c|}{\textbf{Chosen Weights} } & \multicolumn{2}{c}{\textbf{HYCOM}} \\
  & \cellcolor[HTML]{EFEFEF}minimal & nearest & \cellcolor[HTML]{EFEFEF} MBC& NBC & \cellcolor[HTML]{EFEFEF}minimal & nearest \\ \hline
 \# bounces 				& \cellcolor[HTML]{EFEFEF}1 		& 3 		& \cellcolor[HTML]{EFEFEF}1 		& 4 		& \cellcolor[HTML]{EFEFEF}0 	 & 2 \\
 mean OWTT [s] 				& \cellcolor[HTML]{EFEFEF}2.1853 	& 2.1943 	& \cellcolor[HTML]{EFEFEF}4.1812 	& 2.1955 	& \cellcolor[HTML]{EFEFEF}2.1877 & 2.1902 \\
 mean group velocity [m/s] 	& \cellcolor[HTML]{EFEFEF}1436.7 	& 1430.8 	& \cellcolor[HTML]{EFEFEF}750.88 	& 1430.0 	& \cellcolor[HTML]{EFEFEF}1435.1 & 1433.4 \\
 range error [m] 			& \cellcolor[HTML]{EFEFEF}15.4 		& 2.39 	 	& \cellcolor[HTML]{EFEFEF}-1491 	& 0.77 		& \cellcolor[HTML]{EFEFEF}11.9 & 8.30 \\
 \toprule
\end{tabular}
\caption[Further look at algorithm differences for one beacon to beacon pairing]{A comparison of range estimation metrics for each sound speed source and group velocity estimation algorithm on all 10 communication events between North at 30 m \& South at 30 m.}
\label{tab:rangeErrorPostExplanation}
\end{table}
